
```{r}
try(setwd("/Users/rafalopezv/Desktop/R/assignment1/"), silent = TRUE)
try(setwd("/Users/emiliasicari/Desktop/Assignment1/Assignment1/"), silent = TRUE)
source("DataSet1.R")
source("DataSet2.R")
```

---
title: "Assignment1"
author: Rafa and Emilia 
date: 4.3.16
output: ioslides_presentation
---

## Introduction

This presentations summarizes the main findings of two data sets:

- Average heights and weights for American women aged 30-39.
- Number of telephones in various regions of the world

##Women data set: decription
As shown by the function "structure", the data set is composed of two numeric variables, height and weight, and 15 observations. Here it follows some relevant descriptive statistics. 
```{r}
str(women)
```

## Women data set: plots
Using the box plots, we can see that the distribution of the two variables are reasonably symmetric, even though in the case of the variable 'weight', the distribution is concentrated between the 1st and the 2nd quartiles. 
```{r, echo=TRUE}
boxplot(women$height)
boxplot(women$weight)
```
Moreover, the histograms show the distributions of the two variables. In the case of height, density is constant in case of women higher than 60inches. Instead, in the case of weight, density is constant for women weighing less than 50pounds. 
```{r, echo=TRUE}
hist(women$height)
hist(women$weight)
```
Finally, the two variables are highly positively correlated, since correlation is 0.99. Positive correlation is showed by the correlation graph, when height increases, weight increases too. 
```{r, echo=TRUE}
hist(women$height)
hist(women$weight)
```

## Telephones
The datas set "The World's telephones" consists on:

- Number of telephones connections (in thousands)

- Region of the telephones' connections: North America, Europe, Asia, 
  South America, Oceania, Africa, Central America.

- Years: 1951, 1956, 1957, 1958, 1959, 1960, 1961.

## Main findings
Mean, median and standar deviation
```{r, echo=FALSE}
summary1
summary2
```

## Main findings
Mean, median and standar deviation
```{r, echo=FALSE}
summary3
```

#Graph1
```{r, echo=FALSE}
graph1
```

#Graph2
```{r, echo=FALSE}
graph2
```
