---
output: pdf_document
---
```{r}
try(setwd("/Users/rafalopezv/Desktop/R/assignment1/"), silent = TRUE)
try(setwd("/Users/emiliasicari/Desktop/Assignment1/Assignment1/"), silent = TRUE)
source("DataSet1.R")
source("DataSet2.R")
```

---
title: "Assignment1"
author: Rafa and Emilia 
date: 4.3.16
output: ioslides_presentation
---

## Introduction

<<<<<<< HEAD
This presentations summarizes the main findings of two data sets:
- Number of telephones in various regions of the world
- Average heights and weights for American women aged 30-39.

##Women
```{r}
str(women)
```
As shown by the function "structure", the data set is composed of two numeric variables, height and weight, and 15 observations. Here it follows some relevant descriptive statistics. 
>>>>>>> origin/master

The data "Telephones in various regions of the world" contents the following information: 

- Phone users (in thousands)
- Regions
  - North America
  - Europe
  - Asia
  - South America
  - Oceania
  - Africa
  - Central America
- Yeears
  - 1951, 1956, 1957, 1958, 1959, 1960, 1961

## Slide with R Code and Output

```{r}
str(women)
```

## Slide with Plot
Using the box plots, we can see that the distribution os the two variables are reasonably symmetric, even though in the case of the variable 'weight', the distribution is concentrated between the 1st and the second quartile. 
```{r, echo=TRUE}
boxplot(women$height)
boxplot(women$weight)
```

