
---
title: "Assignment1"
author: Rafa and Emilia 
date: 4.3.16
output: ioslides_presentation
---

## Introduction

This presentations summarizes the main findings of two data sets:

- Average heights and weights for American women aged 30-39.
- Number of telephones in various regions of the world

##Women
```{r}
str(women)
```
As shown by the function "structure", the data set is composed of two numeric variables, height and weight, and 15 observations. Here it follows some relevant descriptive statistics. 


## Slide with R Code and Output

```{r}
str(women)
```

## Slide with Plot
Using the box plots, we can see that the distribution os the two variables are reasonably symmetric, even though in the case of the variable 'weight', the distribution is concentrated between the 1st and the second quartile. 
```{r, echo=TRUE}
boxplot(women$height)
boxplot(women$weight)
```

## Telephones
The datas set "The World's telephones" consists on:

- Number of telephones connections (in thousands)

- Region of the telephones' connections: North America, Europe, Asia, 
  South America, Oceania, Africa, Central America.

- Years: 1951, 1956, 1957, 1958, 1959, 1960, 1961.